env_and_copies_stats

### 2023-03-20 code/analysis_code/stats/dust_copies_stats.qmd
stats

@@

##

@@

```{r}
master2<- dust0 %>% full_join(data) %>%
  filter(hr_cst %in% "01") %>%
  select(!c(t1, t7, t13, t19, hr_cst, tsum, t7sum, ...1, SUM, dust,  Type, date )) %>%
  na.omit()
```

@@

@@

```{r}
tidy(growth_fit_bo) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```

## C2: Using all Variables vs. Growth

@@

```{r}
tidy(growth_fit_c2) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```

## RD: Using all Variables vs. Growth

@@

```{r}
tidy(growth_fit_rd) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```

>>>>

# Check Distributions

### Copies per mL

```{r}

#Normal
master %>% 
  ggplot() + geom_histogram(
    aes(
      x = copies_mL)) +
  labs(title = "Non-Log")+ 
  facet_wrap(~site)

#Log-Transformed
master %>% 
  ggplot() + geom_histogram(
    aes(
      x = log(copies_mL))) +
  labs(title = "LOG-TRANS")+ 
  facet_wrap(~site)
```

**We will use the log-transformed data as it has a \~ normal distribution.**

## Log-transform Copies

```{r}
#master <- 
 # master %>%
 # mutate(copies_mL = log(master$copies_mL))
```

@@

@@

```{r}
master2<- dust0 %>% full_join(data) %>%
  filter(hr_cst %in% "01") %>%
  select(site, sal, temp, amm, nn,orthop, copies_mL, t7sum) %>%
  na.omit()
```

@@

#Pull model fit using parsnip()
growth_fit_bo %>%
  extract_fit_parsnip() %>%
  tidy()
```

@@

```{r}
tidy(growth_fit_bo) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```
### Use model to test data

```{r}
aug_test_bo_a <- augment(growth_fit_bo, bo_a)
```

```{r}
rmse <- aug_test_bo_a %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_bo_a %>% rsq(truth = copies_mL, .pred)
bo_a_metrics<- full_join(rmse, rsq)
```

```{r}
bo_a_mod<- lm(copies_mL ~ ., data = bo_a)
AIC(bo_a_mod)
```

```{r}
res_bo_a<- resid(bo_a_mod)
plot(fitted(bo_a_mod), res_bo_a)
abline(0,0)
```
## C2: Using all Variables vs. Growth

@@

```{r}
tidy(growth_fit_c2) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```
### Use model to test data

```{r}
aug_test_c2_a <- augment(growth_fit_c2, c2_a)
```

```{r}
rmse <- aug_test_c2_a %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_c2_a %>% rsq(truth = copies_mL, .pred)
c2_a_metrics<- full_join(rmse, rsq)
```

```{r}
c2_a_mod<- lm(copies_mL ~ ., data = c2_a)
AIC(c2_a_mod)
```

```{r}
res_c2_a<- resid(c2_a_mod)
plot(fitted(c2_a_mod), res_c2_a)
abline(0,0)
```
## RD: Using all Variables vs. Growth

@@

```{r}
tidy(growth_fit_rd) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```
### Use model to test data

```{r}
aug_test_rd_a <- augment(growth_fit_rd, rd_a)
```

```{r}
rmse <- aug_test_rd_a %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_rd_a %>% rsq(truth = copies_mL, .pred)
rd_a_metrics<- full_join(rmse, rsq)
```

```{r}
rd_a_mod<- lm(copies_mL ~ ., data = rd_a)
AIC(rd_a_mod)
```

```{r}
res_rd_a<- resid(rd_a_mod)
plot(fitted(rd_a_mod), res_rd_a)
abline(0,0)
```
